The MRChem MRA code for molecular electronic calculations. Performance and scaling properties

### 2022-05-13 main.tex
Updates from Overleaf

\section{Benchmark results}

In this section we will show how MRChem performs for some simple systems of different size. MRChem is still under development and the results shown here are just a snapshot of the present situation. The goal is not to determine the limitations of the model, but rather to show that at least in some cases it behaves as intended and that the development is going the right way.

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{cccccccccc}
&orbital size& Exchange &  Coulomb & Kinetic energy& Helmholtz & Total \\
 Valinomycine 1E-5& 49 & 71.4& 9.2& 2.7 & 7.4& 97.4\\
Valinomycine 1E-6& 115 & 182.4& 25.3& 6.7 & 21.3&251.2\\
Valinomycine 1E-7& 245 & 442.8& 78.8&17.1& 66.4&644.4  \\
%Valinomycine &1E-8  & 531.0& 163.9& 12.9&32.7& 852.6 \\ older run, different setup
 Gramicidin 1E-5&55&115&18& 4& 8& 164\\
  Gramicidin 1E-6&136&312 & 46& 15 & 26& 429\\
  Gramicidin 1E-7&306& 813&126& 28& 82& 1131\\ %cycle 4
    \end{tabular}
    \caption{Time (in seconds) for different terms in the SCF cycle. Valinomycine using 16 compute nodes and gramicidin 64 compute nodes. The average size (in MB) for one orbital is also given.} %times for cycle 6. 12 MPI/cnode, 4 bank/cnode, 15 OMP
    \label{tab:prec}

@@

>>>>

\section{Benchmark results}
%\todo[inline]{PW: need to explain precision notation mw4, mw5...}
In this section we will show how MRChem performs for some simple systems of different size. MRChem is still under development and the results shown here are just a snapshot of the present situation. The goal is not to determine the limitations of the model, but rather to show that at least in some cases it behaves as intended and that the development is going the right way.

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{cccccccccc}
&orbital size& Exchange &  Coulomb & Kinetic energy& Helmholtz & Total \\
 Valinomycine mw5& 49 & 71.4& 9.2& 2.7 & 7.4& 97.4\\
Valinomycine mw6& 115 & 182.4& 25.3& 6.7 & 21.3&251.2\\
Valinomycine mw7& 245 & 442.8& 78.8&17.1& 66.4&644.4  \\
%Valinomycine &1E-8  & 531.0& 163.9& 12.9&32.7& 852.6 \\ older run, different setup
 Gramicidin mw5&55&115&18& 4& 8& 164\\
  Gramicidin mw6&136&312 & 46& 15 & 26& 429\\
  Gramicidin mw7&306& 813&126& 28& 82& 1131\\ %cycle 4
    \end{tabular}
    \caption{Time (in seconds) for different terms in the SCF cycle. Valinomycine using 16 compute nodes and gramicidin 64 compute nodes. The average size (in MB) for one orbital is also given.} %times for cycle 6. 12 MPI/cnode, 4 bank/cnode, 15 OMP
    \label{tab:prec}

@@

The advantages of the MRA approach is clearer for large systems and/or high precision. We have shown that such large systems are now affordable on large computers.
